Hierarchically Supervised Latent Dirichlet Allocation

### 2011-05-31 paper/main.tex

\subsection{Related Work}

\label{sec:related_work} Latent dirichlet allocation (LDA) is a generative
probabilistic model of corpora that represents documents as a mixed
membership bag-of-words. Also known as topic models, these models
infer the latent structure, or topics, of documents in a corpus. Each
document is represented as a collection of words, generated from a
set of topic assignments (one for each word), where each topic assignment
is drawn from a distribution over topics \citep{Blei2003}.

Supervised latent Dirichlet allocation (sLDA) builds on LDA by incorporating
an exponential family response variable. Although there are many models
for making predictions based on free text, sLDA is unique in that
it is a generative model, it represents documents as a mixed-membership,
and constrains the inference of the latent structure of the documents
by its predictability of the response variable. In other words, sLDA
infers topics such that the model is capable of a high predictive
likelihood for words in a document and the response variable associated
with a document. This approach has been shown to outperform both LASSO
(L1 regularized least squares regression) and LDA followed by least
squares regression \citep{BleiMcAuliffe2008}.

There have been many models that incorporate both latent models of
text and some form of supervision \citep{Ramage2009,DiscLDA,wangbleifeifei08,RelationalLDA}.
One set of models that are particularly relevant to HSLDA are Chang
and Blei's hierarchical models for document networks (Relational Topic
Models). In that family of models, they encountered a similar scenario
where the lack of a link did not truly indicate absence. In hierarchically
labeled data, negative labels are uncommon and the lack of a label
in the hierarchy is not equivalent to a negative label. Therefore,
as in the work of Chang and Blei, we employ regularization to account
for the lack of negative labels. This will be discussed further in
\ref{sec:model}.

% move to related work?
While there have been some attempts to automatically classify groups
of patients as a potential preliminary step to ICD-9 code assignment
\citep{Ruch2008,FreitasJunior2006,RibeiroNeto2001,Brown2006}, fully
automatic assignment of ICD-9 codes to medical text became a more
prevalent research topic only in the last few years. A subset of earlier
work proposed various methods on small corpora, based on a few specific
diseases \citep{Rao2003} but the most recent and promising work on
the subject was inspired by the 2007 Medical NLP Challenge: {}``International
Challenge: Classifying Clinical Free Text Using Natural Language Processing\textquotedblright{}
(website). Most of the classification strategies included word matching
and rule-based algorithms. \citep{Goldstein2007,Crammer2007,Farkas2008}.
The data set given to the participants consisted only of documents
that were 1-2 lines each and all of the documents were radiology reports
- clearly limiting the scope of potential ICD-9 codes which could
be assigned. The only paper which has attempted to work with a document
scope as large as ours was the 2008 Lita et al publication \citep{Lita2008}.
Lita proposed support vector machine and bayesian ridge regression
methods to assign appropriate labels to the documents but did not
utilize the ICD-9 hierarchy to leverage more comprehensive predictions.

@@

\section{Inference}
\label{sec:inference}
\input{inference}
\section{Experiments}

>>>>

@@

\section{Inference}
\label{sec:inference}
\input{inference}

\section{Related Work}

\label{sec:related_work} 
\input{related_work}

\section{Experiments}
